% resume.tex
% vim:set ft=tex spell:

\input{Preamble}

% and the actual content starts here
\begin{document}

\input{Me}

\hyphenation{using}

\makeresumesection{Core Technical Skills}{
    \input{Skills/Generic}
}{0em}

\makeresumesection{Experience}{
    \begin{itemize}
            \parskip=0em
    {\item
        \headerrow
	    {\textbf{Quality Engineer (SDET)}}
            {\textbf{Ansible by Red Hat}}
        \\
        \headerrow
            {\emph{July 2019 -- Present}}
            {\emph{Portland, OR}}
        \begin{itemize*}
	\item Automated testing for Ansible Tower 3.6 and 3.7 using Jenkins, Python, and Bash scripts.
	\item Tested the Tower Ansible Collection as part of the effort to convert it from an unsupported project to a supported project.
	\item Led the testing effort for the Receptor core project using Golang to write automated tests
        \end{itemize*}}
    {\item
        \headerrow
            {\textbf{System Administrator}}
            {\textbf{Ormuco}}
        \\
        \headerrow
            {\emph{September 2017 -- May 2018}}
            {\emph{Portland, OR}}
        \begin{itemize*}
        \item Automated the deployment of OpenStack public and private clouds using Kolla.
        \item Designed, maintained, and upgraded multiple Ceph clusters based on client needs.
        \item Performed storage cluster performance testing in order to decide on QoS limitations.
        \end{itemize*}}
    {\item
        \headerrow
            {\textbf{Cloud Intern/Developer Advocate Intern}}
            {\textbf{DreamHost}}
        \\
        \headerrow
            {\emph{August 2015 -- September 2017}}
            {\emph{Portland, OR}}
        \begin{itemize*}
        \item Automated the publication workflow for DreamCompute and DreamObjects documentation using Bash, Python, and Jenkins.
        \item Updated the DreamHost Forum to run on Discourse while preserving existing data.
        \item Contributed to several OpenStack projects including Shade, API Site, and OpenStack Manuals.
        \item Copresented a 40 minute talk “From Upstream Documentation To Downstream Product Knowledge Base” at the 2016 OpenStack Summit in Austin, Texas.
        \end{itemize*}}
    {\item
        \headerrow
            {\textbf{System Administrator/Tech Support}}
            {\textbf{The Computer Action Team}}
        \\
        \headerrow
            {\emph{October 2014 -- September 2017}}
            {\emph{Portland, OR}}
        \begin{itemize*}
        \item Administered Linux lab computers, compute servers, Solaris and FreeBSD file servers, package mirrors, web servers, and a 3 node Ganeti cluster as part of the Linux/UNIX team with Ansible, Puppet, and Bash scripts.
        \item Trained new junior system administrators on administering Linux and UNIX systems.
        \end{itemize*}}
        \end{itemize}
}{0em}

\makeresumesection{Major Projects}{
    \begin{itemize}
            \input{Projects/apt-package-mirror}
    \end{itemize}
}{0em}

\makeresumesection{Education}{
    \begin{itemize}
    {\item
      \headerrow
        {\textbf{B.S. in Computer Science}}
        {\textbf{Portland State University}}
      \\
      \headerrow
        {\emph{Cum Laude}}
        {\emph{2014 - 2019}}
    }
    \end{itemize}
}{0em}

\hrule

\end{document}
